---
title: "Lab 2"
author: "Omima Hassan"
date: "9/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)
```
## Question Set Individual

**For each of the questions below provide at least one graphic as a basis for your answer.**

1. How are ratings distributed? Don't forget to mention outliers, if there are any.
* Raings are distributed based on the amount of chocolates that were sold. The average ratings for chocolates ranged from 2.5 to 3.5 stars while outliers included ratings of 5 and 1.
```{r}
library(classdata)
hist(choco$Rating, xlab = "Chocolae Rating", ylab = "Amount Sold", main = "Histogram of chocolate ratings")
```


2. Do ratings depend on the cocoa percentage of a chocolate bar? 

* Ratings don't depend on the cocoa percentage

```{r}
plot(choco$Rating , choco$Cocoa.Pct, xlab = "Chocolate Rating", ylab = "Chocolate Percentage", main = "Chocolate Rating with Choclate Percentage")
```


3. What class is the variable representing company locations? How is this different from a 'character' variable?

* Company represents a factor variable.

* A factor variable is different from a character in that it stores a text value as a number, so in this example each company would have an associated number that can also be used to represent it.

```{r}
class(choco$Company)
```